\section{\gls{T11} Retrospective}

In our retrospective of sprint 4 we discussed how the final sprint went.

\subsection{Issues from the previous sprint}
The primary issue from the previous sprint was regarding or planning, we had taken to many tasks, but also took to many tasks on the fly from the other groups.
The estimation of how many tasks we could take, showed to be better than the previous sprint, we attempted at a more conservative estimation where we , but less external tasks came to our group as well. Though we did still not estimate correctly it was more accurate than the previous  sprints. This was close enough for us to decide not to employ new measures, but continue the same way again and see if with time it gets more accurate.

\subsection{Issues this sprint}
One of the things we discussed this sprint was that we did not utilize our time at supervisor meetings well enough. We some group members felt that to much time was spent on non-meeting related topics. This could be things like jokes or elaborating on technical details which were not related to the topics we wanted feedback on. This was not a majore issue, but an area where we could optimize or time efficiency.
We discussed that we could make a more formal meeting structure, maybe even make a document describing how we prefer a meeting to proceed. This could be shared with the supervisor as well, so that the supervisor is included in our thoughts, but also so that the supervisor is able to make amendments if he or she has some preferences to include as well.

\subsection{Things that went well}
We were satisfied with how our collaborations went we have had no internal conflicts and we contributed an appropriate amount to the Giraf project. 
