\section{\gls{T11} Retrospective}

In our retrospective of sprint 4 we discussed how the final sprint went.

\subsection{Issues from the previous sprint}
The primary issue from the previous sprint was regarding or planning, we had taken to many tasks, but also took to many tasks on the fly from the other groups.
We managed to make a better estimation of how many tasks we could take compared to last sprint. We attempted with a more conservative approach where we allocated a little more time for each task than we did previously. Another factor that helped was that fewer external tasks came to our group as well. We still did not estimate correctly, but it was more accurate than the previous sprints. It was accurate enough for us to decide not to employ new measures, but continue this way again and see if with time it gets more accurate when we have more experience.

\subsection{Issues this sprint}
One of the things we discussed this sprint was that we did not utilize our time at supervisor meetings well enough. Some group members felt that too much time was spent on non-meeting related topics. This could be things like jokes or elaborating on technical details which were not related to the topics we wanted feedback on. This was not a major issue, but an area where we could optimize our time efficiency.
We discussed that we could make a more formal meeting structure, maybe even make a document describing how we prefer a meeting to proceed. This could be shared with the supervisor as well, so that the supervisor is included in our thoughts, but also so that the supervisor is able to make amendments if he or she has some preferences to include as well.

\subsection{Things that went well}
We were satisfied with how our collaborations went we have had no internal conflicts and we contributed an appropriate amount to the \gls{giraf} project. 
