\section{Review}
%Summer
% What have been done
% Status now
The Giraf project groups started off with features for the Xamarin project. But it was quickly realized that the Xamarin ecosystem was disallowing a lot of the developers to actually work. Since the Xamarin has abandoned Linux support a couple of years back. Since there were roughly 40\% of the developers on the Giraf project running Linux it was a major issue that Xamarin didn't support Linux.

Because of this, the front-end meta group decided to move to Flutter. At the end of Sprint 1 the transition from Xamarin to Flutter where not at a release ready state. The status of the new Flutter app was that the Core was more or less implemented, by core we mean the architecture, data models, API module and some basic screen where implemented.

Within Sprint 1 the first alpha version of the Flutter app core where released to the developers and the PO group had prepared new user stories for the developer teams to tackle. The developers behind the alpha core held a release presentation where all developers of the Giraf project where present. This presentation was an introduction to Flutter, the architecture of the new core and a coding session where a user story where implemented. Afterward, the remaining user stories were delegated to each developer team. Leaving roughly one week off before the end of the sprint. The short timeline, of course, resulted in most developer teams not being able to finish their story before the end of the sprint. Never the less the overall feedback was that the developers were happy with the transition to Flutter, they feld that the development where more rapid and the UI was easier to implement. Most groups were almost finished with their stories, but most of them were blocked by a number of lacks in the core mainly: The ability to "send" data from one feature to another, The ability to implement widget tests and a bug in the authentication system.

The PO group where satisfied with the progression doing this sprint, taking into account the need to switch to Flutter. The PO group considered the move to Flutter an elimination of serious technical depth and thereby improving the quality of the product quite a lot.