\section{Group process}

In addition to the \gls{G19} process, we have defined our own internal process.
This process defines how we intend to work as a group, and which practices we intent to uphold. 

We intent to work in the \gls{XP} spirit, with focus on some of the practices, and the core values.
The central practices we want to focus on, are as follows:
\begin{itemize}
    \item Pair programming 
    \item Test driven development
    \item Sustainable pace
\end{itemize}

It is important to us, that the work done is of good quality, and the members of our team share knowledge. The pair programming is meant to ensure quality, because it makes it possible to get different thoughts on a solution, and because the \gls{driver} can get imitate code review.
The test driven development is meant to ensure code quality because it makes sure that the code works as intended, it makes it easier to find later bugs, and it works as later documentation for the code. 
We find the sustainable pace practice especially important to uphold, because all of our team members have had experience with having a workload that is too big, and therefore know firsthand the problems associated with this. 
For this practice, we have designed a schedule, where we calculate the amount of hours that should be used for project work every week. This corresponds to forty hours minus the time dedicated to other classes. We then note how many hours each day the different group members work, and make sure that they never work more than the forty hours in total. Some of the hours we work will be on location, so we can help each other, and work with other groups, and some will be up to each individual team member.

Apart from the \gls{XP} practices, we have also made some agreements. 
One of these is that the related documentation should always be produced in the context of the event or work it reflects. This way we will not forget important details, or make knowledge implicit when it should not be. 
We will have daily standup meetings, so everybody knows how the work is progressing. 
In the end of every \gls{SOSSprintRetrospective}, we hold our own retrospective, to improve our internal process. Here we will make necessary changes to our process. 
